---
title: "Project_MLR"
author: "Group 6"
date: "November 29, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About Multilinear Regression Model
After looking at all the variables included in the dataset, we decided to test the predictability for the variance of Rent by four main variables. 

- Dependent Variable: Rent
- Potential Independent Variables: Image Count, Num of Bedrooms, Income, Metro Distance
- Step1: Select variables using stepwise regression
- Step2: Analyse the best-fitting regression model


## Preparation: Smell Test & Datatype Check
```{r, echo=FALSE}
rent <- read.csv("apartments_nonull.csv", header = TRUE,sep = ",")   
summary(rent)

par(mfrow=c(2,2))
hist(rent$Image.count)
hist(rent$Metro.Distance)
hist(rent$Num.bedrooms)
hist(rent$Income)

library(gplots)
par(mfrow=c(2,2))
distance_price <- lm(Rent~log(Metro.Distance), data = rent)
plot(Rent~log(Metro.Distance), data = rent)
abline(distance_price)

income_price <- lm(Rent~Income, data = rent)
plot(Rent~Income, data = rent)
abline(income_price)

bedrooms_price <- lm(Rent~Num.bedrooms, data = rent)
plot(Rent~Num.bedrooms, data = rent)
abline(bedrooms_price)

image_price <- lm(Rent~Image.count, data = rent)
plot(Rent~Image.count, data = rent)
abline(image_price)
```

## Step1: Stepwise Regression
From the initial exploration above, it's obvious that the distribution of Metro Distance is left-screw. To fix that, We decided to put log(Metro.Distance) into stepwise regression instead of Metro.Distance. 

From the simple linear regression plots, we can reasonably expect that the Image count would be kicked off from model.

The codes tell R to start with the null model and search through models lying in the range between the null and full model using the forward selection algorithm.

```{r, echo=FALSE}
null <- lm(Rent~1, data=rent)
full <- lm(Rent~ Income + log(Metro.Distance) + Image.count + Num.bedrooms, data = rent)
stepwise <- step(null, scope=list(lowr=null,upper=full), direction="both") 
#It tells R to start with the null model and search through models lying in the range between the null and full model using the forward selection algorithm.
```


## Summary of Step1:

```{r, echo=FALSE}
summary(stepwise)
```


## Step2: Analyse the Model 

```{r, echo=FALSE}
fitting.slr<-lm(formula = Rent ~ Num.bedrooms + Income + log(Metro.Distance), data = rent)
summary(fitting.slr)
require(heplots)
etasq(fitting.slr,anova=TRUE,partial=FALSE)
```


## Compare the full model with the new model: 

```{r, echo=FALSE}
full <- lm(Rent~ Income + log(Metro.Distance) + Image.count + Num.bedrooms, data = rent)
new <- lm(Rent~ Income + log(Metro.Distance) + Num.bedrooms, data = rent)
anova(full, new, test="Chisq")
# Chisq test: to test whether reduction in the residual sum of squares are statistically significant.
#p-value > 0.05, the new model is not significantly different from the old model.
```